---
title: "case_study"
author: "Jinghan Zhao"
date: "2024-10-08"
output: html_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


```{r}
library(p8105.datasets)
library(leaflet)

data(nyc_airbnb)
```

## Brainstorm questions

* Where are max and min air bnb prices?
  * What are average prices?
  * What factors affect prices?
* Where are prices going up and down over time?
* What's the relationship between number of reviews and average review?
* Does room type affect availability?
* What's the location of the unit?
  * What areas are popular?
  * Popularity = number of units? Average price?
* Are there repeat hosts?
  * If so, what does that mean?

```{r}
nyc_airbnb %>% 
  select(price) %>% 
  min()

nyc_airbnb %>% 
  select(price) %>% 
  max()

nyc_airbnb %>% 
  pull(price) %>% 
  mean()
```

```{r}
nyc_airbnb %>%
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = room_type, y = availability_365)) +
  geom_violin()
```

```{r}
nyc_airbnb |>
  group_by(room_type) |>
  summarize(mean_price = mean(price))
```

```{r}
nyc_airbnb %>%
  filter(calculated_host_listings_count > 5) %>%
  distinct(host_id, host_name, calculated_host_listings_count) %>% 
  arrange(desc(calculated_host_listings_count))
```

```{r}
nyc_airbnb %>%
  group_by(neighbourhood_group) %>%
  summarise(total_reviews = sum(number_of_reviews, na.rm = TRUE)) %>%
  arrange(desc(total_reviews))
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(median_price = median(price)) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

star rate VS price

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point()
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan",
         price < 1000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .1)
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan",
         price < 1000,
         room_type == "Entire home/apt") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price)) %>% 
  arrange(desc(mean_price))
```


```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan",
         price < 1000,
         room_type == "Entire home/apt") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle= 45, vjust = 1, hjust = 1))
```

Useful package for good maps: `leaflet`

To interact with maps, output html

```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location)

nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan",
         price < 1000) %>% 
  slice(1:1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(
    ~lat, ~long, 
    color = ~pal(review_scores_location), 
    radius = 2)
```

